% !TEX root = ../main.tex
% !TEX program = lualatex
\documentclass[../main.tex]{subfiles}
\IfSubfilesClassLoaded{\externaldocument{\subfix{../build/main}}}{}
% =============================================================================
% CHAPTER 4: NAVWAR ENTERPRISE AND WARFARE CENTERS
%
% DESCRIPTION: This chapter provides an overview of the NAVWAR enterprise,
%              including its headquarters directorates, Field Readiness
%              Directorates (FRDs), and associated warfare centers.
% =============================================================================

\begin{document}
\ifSubfilesClassLoaded{\chapter{EDO Study Guide}}{}
%====================
% Contents here
%====================

% === NAVWAR ===
\section{NAVWAR Enterprise and Warfare Centers}
\minibib
\subsection{HQ Directorates and FRD}
\Tab{\ref{tab:navwar-offices}} lists\ac{navwar} HQ directorates and\acp{frd} with one-line roles.

\begin{longtblr}[%
  caption = {NAVWARHQ directorates and Field Readiness Directorates -- one-line roles.},%
  label   = {tab:navwar-offices},%
  entry   = {NAVWAR HQ Directorates and FRDs},%
  remark{Source} = {\tabCite{edo-2-1-3-navwar-enterprise-2024}}
]{colspec = {@{} F L W @{}}}
  \toprule
  {Code}        & {Office}                         & {One-liner}\\
  \midrule
  1.0           & Comptroller                      & Budget formulation/execution; BSO duties; funds control and financial reporting.\\
  2.0           & Contracts                        & Contracting policy/oversight; acquisition strategy; award/administration of instruments.\\
  3.0           & Counsel                          & Legal counsel for acquisition/ethics; protests, claims, agreements, and compliance.\\
  4.0           & Logistics \& Fleet Support       & Life-cycle logistics; sustainment planning; supply/tech data; fleet support integration.\\
  5.0           & Chief Engineer / TA (Cyber)      & Technical standards/architecture; interoperability; cyber TA; certification/air-gapping where required.\\
  6.0           & Program Management               & Program governance; milestone readiness; portfolio integration; interface with PEOs.\\
  7.0           & Science \& Technology            & S\&T portfolio; experimentation/prototyping; tech transition to programs of record.\\
  8.0           & Corporate Operations             & Workforce, security, facilities, enterprise information-technology/chief-information-officer services, PAO, and other corporate enablers.\\
  \midrule
  FRD-100       & Fleet Support                    & Sustainment services and distance support; field engineering and readiness assistance.\\
  FRD-200       & Installations                    & C4I installation planning/execution; shore/afloat integration and cutover support.\\
  \bottomrule
\end{longtblr}

\subsection{Warfare Centers (alphabetical)}
\Tab{\ref{tab:navwar-centers}} lists\ac{navwar} Warfare Centers with locations and descriptions.

\begin{longtblr}[%
  caption = {NAVWAR Warfare Centers with locations and descriptions.},%
  label   = {tab:navwar-centers},%
  entry   = {NAVWAR Warfare Centers},%
  remark{Source} = {\tabCite{edo-2-1-3-navwar-enterprise-2024}}%
]{%
  colspec = {@{} F L L @{}}%
}
  \toprule
  {Center}  & {Location}      & {Description} \\
  \midrule
  NIWC LANT & Charleston, SC  & Enterprise information-technology solutions; cradle-to-grave C4ISR. \\
  NIWC PAC  & San Diego, CA   & C4ISR RDT\&E; Navy/Joint/Allied support. \\
  NSFA      & Chantilly, VA   & Navy link to the NRO; space research and development coordination. \\
  \bottomrule
\end{longtblr}

\paragraph{NIWC LANT detachments}
\begin{itemize}
	\item \textbf{HQ:} Charleston, SC.
	\item New Orleans, LA.
	\item Norfolk, VA.
	\item Naples, Italy.
	\item Manama, Bahrain.
\end{itemize}

\paragraph{NIWC PAC detachments}
\begin{itemize}
	\item \textbf{HQ:} San Diego, CA.
	\item Everett, WA.
	\item Pearl City, HI.
	\item Santa Rita, Guam.
	\item Yokosuka, Japan.
\end{itemize}
%====================
% End of file
%====================
\ifSubfilesClassLoaded{
  \renewcommand*{\entryname}{\textbf{\color{Modern} Acronym}}
  \renewcommand*{\descriptionname}{\textbf{\color{Modern} Definition}}
  \printnoidxglossary[
    type=\acronymtype,
    title=Acronyms,
    style=long-booktabs
]}{}
\end{document}

