% !TEX root = ../main.tex
% !TEX program = lualatex
\documentclass[../main.tex]{subfiles}
\IfSubfilesClassLoaded{\externaldocument{\subfix{../build/main}}}{}
% =============================================================================
% APPENDIX: EDO FLAG OFFICERS
%
% DESCRIPTION: This appendix provides a snapshot of Engineering Duty Officer
%              (EDO) flag officers and their billets. This information is
%              time-sensitive and should be verified before use.
% =============================================================================

\begin{document}
\ifSubfilesClassLoaded{\chapter{EDO Study Guide}}{}
%====================
% Contents here
%====================
\section{EDO Flag Officers (snapshot)}
\emph{\footnotesize Verify names/billets the week of your board. Current as of: 13 Nov 2025.}

\subsubsection*{Vice Admirals}
\begin{description}[style=nextline, labelsep=0.5em, font=\bfseries]
	\item[\textbf{VADM James P.\ Downey.}]
	\ac{comnavsea}; leads the $80$K-person naval shipbuilding enterprise and chairs the Navy Program Executive Council for ships and ship systems.\srcCite{edo-3-3-1-acq-policy-players-2025}
	\item[\textbf{VADM Johnny R.\ Wolfe Jr.}]
	Director, \ac{ssp}, responsible for the nation’s strategic weapons industrial base and Fleet ballistic missile sustainment.\srcCite{edo-3-3-1-acq-policy-players-2025}
	\item[\textbf{VADM Seiko Okano.}]
	\ac{pmildep} to \ac{asnrdanda}; retains direct reporting program manager duties for Project Overmatch and NAVWAR’s digital architecture initiatives.\srcCite{DVIDS-Overmatch-OpenDAGIR-2025}
\end{description}

\subsubsection*{Rear Admirals (Upper Half)}
\begin{description}[style=nextline, labelsep=0.5em, font=\bfseries]
	\item[\textbf{RADM Casey J.\ Moton.}]
	\ac{peocvn}, accountable for aircraft carrier new construction and in-service nuclear availability portfolios.\srcCite{edo-3-3-1-acq-policy-players-2025}
	\item[\textbf{RADM Kurt J.\ Rothenhaus.}]
	\ac{cnr} and Commander, ONR Global, aligning S\&T investments with fleet needs.\srcCite{edo-3-3-1-acq-policy-players-2025}
	\item[\textbf{RADM Jonathan E.\ Rucker.}]
	\ac{peossn}, responsible for submarines, undersea weapons, and the Columbia/Virginia Class Program Offices.\srcCite{edo-3-3-1-acq-policy-players-2025}
	\item[\textbf{RADM Brian A.\ Metcalf.}]
	\ac{peoships}, leading the surface combatant, amphibious, and auxiliary ship portfolios.\srcCite{edo-3-3-1-acq-policy-players-2025}
	\item[\textbf{RADM Douglas L.\ Williams.}]
	Director for Test, \ac{mda}, synchronizing joint missile defense T\&E campaigns.\srcCite{edo-3-3-1-acq-policy-players-2025}
\end{description}

\subsubsection*{Rear Admirals (Lower Half)}
\begin{description}[style=nextline, labelsep=0.5em, font=\bfseries]
	\item[\textbf{RDML Peter D.\ Small.}]
	\ac{navsea} Chief Engineer / Commander, \ac{nswc}/\ac{nuwc}, the Navy’s lead technical authority for ship systems.\srcCite{edo-3-3-1-acq-policy-players-2025}
	\item[\textbf{RDML Dan L.\ Lannamann.}]
	\ac{cnrmc}, overseeing regional maintenance centers and private-sector depot availabilities.\srcCite{edo-3-3-1-acq-policy-players-2025}
	\item[\textbf{RDML Kevin R.\ Smith.}]
	\ac{peousc}, accountable for unmanned surface and small combatant shipbuilding programs.\srcCite{edo-3-3-1-acq-policy-players-2025}
	\item[\textbf{RDML Dianna Wolfson.}]
	Fleet Maintenance Officer, \ac{usff}, integrating ship maintenance execution and TYCOM readiness.\srcCite{edo-3-3-1-acq-policy-players-2025}
	\item[\textbf{RDML Daniel W.\ Ettlich.}]
	Director, Fleet Maintenance, \ac{pacflt}, leading west-coast and forward-deployed maintenance readiness.\srcCite{edo-3-3-1-acq-policy-players-2025}
\end{description}

\subsubsection*{Reserve EDO Flags}
\begin{description}[style=nextline, labelsep=0.5em, font=\bfseries]
	\item[\textbf{RDML Robert J.\ Dodson (USNR).}]
	Deputy Commander, Supervision of Shipbuilding (SUPSHIP), \ac{navsea}, aligning reserve expertise to construction oversight.\srcCite{edo-3-3-1-acq-policy-players-2025}
	\item[\textbf{RDML Michael S.\ Richman (USNR).}]
	Deputy Director, Regional Strike Systems, \ac{ssp}, supporting strategic weapons sustainment.\srcCite{edo-3-3-1-acq-policy-players-2025}
\end{description}
%====================
% End of file
%====================
\ifSubfilesClassLoaded{
  \RenewDocumentCommand{\entryname}{}{\textbf{\color{Modern} Acronym}}
  \RenewDocumentCommand{\descriptionname}{}{\textbf{\color{Modern} Definition}}
  \printnoidxglossary[
    type=\acronymtype,
    title=Acronyms,
    style=long-booktabs
]}{}
\end{document}

